Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-05-14 paper.tex
Fixed the order of affiliations (I hope). Two affiliations remain missing.

\address{%
   \iid(1)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden\\
    \iid(2)National Institute of Health, Somewhere in the US, USA\\
    \iid(5)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland\\
    \iid(6)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK\\
    \iid(7)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK\\
    \iid(8)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia\\
    \iid(1)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(10)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA\\
   \iid(3)NIH, Somewhere in the US, USA\\
    \iid(12)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ    08854, USA \\
    \iid(13)Gorlaeus Laboratories, Leiden University, 2333 CC Leiden,    The Netherlands \\
    \iid(14)Department of Chemistry, University of Washington, Seattle, WA 98195
}%

>>>>

\address{%
    \iid(1)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(2)National Institute of Health, Somewhere in the US, USA \\
    \iid(3)... \\
    \iid(4)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(5)Gorlaeus Laboratories, Leiden University, 2333 CC Leiden, The Netherlands \\
    \iid(6)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(7)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(8)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(9)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(10)... \\
    \iid(11)Department of Chemistry, University of Washington, Seattle, WA 98195 \\
    \iid(12)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA \\
    \iid(13)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden
}%
